### 2021-06-03 paper/model/testing.tex
Update testing section to include rapid tests.

We support to model testing as consisting of three stages. Firstly, we model who demands
a test. Demand functions map from individual characteristics to a probability which is
the probability for this individual to demand a test. There can be multiple demand
functions where each function may describe a different channel. For example, individuals
who experience symptoms or have a risk contact may ask for a test. Or, the ministry of
education requires a negative test result from every teacher every second week. After
the probabilities for each individual and every demand model are computed, individuals
who demand a test as well as the channel is sampled.

@@

>>>>

Our model includes both PCR tests which are scarce and take time until the result becomes
available and rapid tests which are done after an individual's contacts are determined
but before the contacts take place.

PCR testing consists of three stages. Firstly, we model who demands a PCR test. Demand
functions map from individual characteristics to a probability which is the probability
for this individual to demand a test. There can be multiple demand functions where each
function may describe a different channel. For example, individuals who experience
symptoms or have a risk contact may ask for a test. Or, the ministry of education
requires a negative test result from every teacher every second week. After the
probabilities for each individual and every demand model are computed, individuals who
demand a test as well as the channel is sampled.

@@

Rapid tests are modeled much simpler. Every day before individuals have contacts they can
decide to be tested. For example students that plan to attend school that day and have
not done a rapid test in the last three days get a rapid test. Then they immediately
receive the test result. After they have received their test result individuals can react
to it by reducing their contacts. For example positively tested individuals may not go to
work and reduce their household contacts to some degree. Who reduces their contacts to
what degree depends on a quarantine compliance attribute.

Our rapid tests include false positives and false negatives. The sensitivity of rapid tests in our model depends on when the individual has
or will become infectious. This way we can account for the fact that rapid tests are
likely to be false positive before infectiousness starts.
